Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 experiments.tex
started pass over 3

\subsection{WHO Variants}
\label{sec:variations}
To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants. Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin. However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.

We also calibrated the various methods

In the experiment, we compared the performance of HOG, WHO, WHO-CG, WHO-CG-Z and NZ-WHO. The WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}

The experiment results is on Tab.~\ref{tab:who_initializations}
We found out that without calibration, NZ-WHO performs the best on object
detection on 3DObject car dataset \cite{Savarese07}. See Table
\ref{tab:who_initializations} for detail. In essence, if we use calibration, we
could achieve better performance but since our goal is to do 2D-3D matching and
continuous viewpoint estimation using on-the-fly template generation, we did not
calibrated our templates.

We empirically found out that NZ-WHO performs reasonably well without time
consuming calibration stage compare to other variational method to generate
templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
elevations. Each template takes approximately 80 milliseconds to generate a
NZ-WHO template. We also calibrated templates using the method presented in
\cite{Aubry14}. The calibration learns affine transformation of the detection
confidence.% Note that in Section \ref{experiments}, we provide the same
% experiment with 9 CAD models.

\begin{table}[!htbp]
    \footnotesize
    \setlength{\tabcolsep}{1pt}
    \centering
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
\hline
\end{tabular}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table}

@@

\begin{figure}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{cc}
  \hline
  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
  \hline
\end{tabular}
\caption{Average Precision (AP) and Average Viewpoint Precision (AVP)
  and viewpoint confusion table on PASCAL 12 car validation set using
  R-CNN + Ours (full). From the top left, 4 views, 8 views, 16 views and 24 views. Since our method only augment the object detection, the AP remains the same for all cases. As we increase the viewpoint estimation, the AVP decreases. Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
  \label{fig:car_cnn_ap}
\end{figure}

>>>>

\subsection{WHO Variants}
\label{sec:variations}
To validate our approach, we run an ensemble of NZ-WHO templates as a
bank of exemplar detectors and compare its performance with other WHO
variants, notable WHO~\cite{Hariharan12} and the original non-whitened
HOG~\cite{Dalal05}. In addition, we evaluate WHO-CG and WHO-CG-Z:
WHO-CG uses iterative Conjugate Gradient method to generate
WHO. WHO-CG-Z whitens the whole template, but zeros out textureless
region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using
iterative Conjugate Gradients  (our method).

Tab.~\ref{tab:who_initializations} gives the correponding results for
the various methods on a subset of the 3D Object Classes car
dataset~\cite{Savarese07} (all images corresponding to one particular
car instance, seen from different viewpoints), reporting 3 quantities:
detection performance in average precision (AP), pose estimation in mean
precision in pose estimtation (MPPE), and the respective runtime.
%
For all methods, the table gives the results with and without
calibration, using the calibration method of~\cite{Aubry14}. This
calibration learns affine transformation of the detection confidence.
For each method, we generated templates for 1 CAD model exemplar
rendered from 24 azimuth and 4 elevation angles.
% Since WHO variants uses HOG features, they are slower than
% HOG templates but WHO variants in general performs better than WHO by
% significant margin. However, WHO using Cholesky decomposition with
% Gaussian Elemination takes the most time yet performs worse than
% NZ-WHO which is two order of magnitude faster to generate.

\paragraph{Results.}
In Tab.~\ref{tab:who_initializations}, we observe that, on average,
calibration indeed improves performance in terms of AP, sometimes
drastically (e.g., from $54.4$ to $92.8$ for WHO-CG-Z), as observed in
prior work~\cite{Aubry14}. At the same time, calibration is
computationally expensiv, resulting in runtimes that are two orders of
magnitudes larger than without calibration. Strikinly, our method
NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
ms vs. 8.7 s when using calibration.

% We empirically found out that NZ-WHO performs reasonably well without time
% consuming calibration stage compare to other variational method to generate
% templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4
% elevations. Each template takes approximately 80 milliseconds to generate a
% NZ-WHO template. We also calibrated templates using the method presented in
% \cite{Aubry14}. e.% Note that in Section \ref{experiments}, we provide the same
% % experiment with 9 CAD models.

\begin{table}[!htbp]
    \footnotesize
    \setlength{\tabcolsep}{1pt}
    \centering
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG {\em (ours)}  & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
\hline
\end{tabular}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table}

@@

\begin{figure}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{cc}
%  \hline
  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
%  \hline
\end{tabular}
\caption{Average Precision (AP) and Average Viewpoint Precision (AVP)
  and viewpoint confusion table on PASCAL 12 car validation set using
  R-CNN + Ours (full). From the top left, 4 views, 8 views, 16 views and 24 views. Since our method only augment the object detection, the AP remains the same for all cases. As we increase the viewpoint estimation, the AVP decreases. Note that since we estimate null viewpoint if our method fails to find match, there are more 0 viewpoint predictions (top row of confusion matrices) }
  \label{fig:car_cnn_ap}
\end{figure}
